The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
residential composition

Next, looking at measures of Happiness and Health, we found that generally as happiness and health increase, social fear decreases. This is shown in @fig-FearHappiness and @fig-FearHealth.

@@

Next, looking at residential composition and race combined displayed in @fig-FearNeighborhood, we do notice a pattern where respondents living in residentially more diverse areas were more likely to respond affirmative to the question of social fear.

>>>>

Next, looking at residential composition and race combined displayed in @fig-FearNeighborhood, we do notice a pattern where respondents living in residentially more diverse areas were more likely to respond affirmative to the question of social fear. This indicates the sentiment that respondents felt safer and more comfortable living in neighborhoods where other residents share their racial identities, which speaks to

What's more, looking at measures of individual-level characteristics like Happiness and Health, we found that generally as happiness and health increase, social fear decreases. This is shown in @fig-FearHappiness and @fig-FearHealth. This finding resonates with recent scholarship on the direct relationship between fear of crime and subject well-being that higher levels of happiness and better physical health are associated with lower levels of fear [@krulichova2018].

@@
